---
title: 
author: 
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Packages
library(tidyverse)
library(here)
# Parameters
  file_data <- here("/data/mbc_data.rds")
#===========================================================================

# Code
  df <- read_rds(file_data)
```

## K2SO4 0.05 M Extractable DOC
```{r DOC, echo=FALSE, warning = FALSE}
p1 <- ggplot(df, aes(treatment, fum_C_mg_g)) + 
  geom_boxplot(aes(treatment, fum_C_mg_g, fill = day)) + 
  facet_wrap(litter~water_content, nrow = 2, scales = "fixed") + 
  geom_point(aes(treatment, fum_C_mg_g, fill = day), 
             position = position_jitterdodge(jitter.width = 0.1),
             alpha = 0.5, size = 2, shape = 21) +
  labs(x = "Preincubation treatment", y = "Extractable DOC (mg/g soil)") +
  theme_bw() + scale_fill_brewer(palette = "Set1")
p1
```

## Microbial biomass C
```{r MBC, echo = FALSE, warnings = FALSE}
p3 <- ggplot(df, aes(treatment, MBC_mg_g_soil)) + 
  geom_boxplot(aes(treatment, MBC_mg_g_soil, fill = day)) + 
  facet_wrap(litter~water_content, nrow = 2, scales = "fixed") + 
  geom_point(aes(treatment, MBC_mg_g_soil, fill = day), 
             position = position_jitterdodge(jitter.width = 0.1),
             alpha = 0.5, size = 2, shape = 21) +
  labs(x = "Preincubation treatment", y = "Microbial biomass C (mg/g soil)") +
  theme_bw() + scale_fill_brewer(palette = "Set1")
p3
```

## Extracted and fumigated C
```{r fumigated, echo = FALSE, warnings = FALSE}
p2 <- ggplot(mbc_data, aes(treatment, unfum_C_mg_g)) + 
  geom_boxplot(aes(treatment, unfum_C_mg_g, fill = day)) + 
  facet_wrap(litter~water_content, nrow = 2, scales = "fixed") + 
  geom_point(aes(treatment, unfum_C_mg_g, fill = day), 
             position = position_jitterdodge(jitter.width = 0.1),
             alpha = 0.5, size = 3, shape = 21) +
  labs(x = "Preincubation treatment", y = "Extractable and fumigated C (mg/g soil)") +
  theme_bw() + scale_fill_brewer(palette = "Set1")
p2
